Results

### 2019-06-03 Manuscript_draft/Results.Rmd
edits

lambda <- c(stigma_type[1], selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_surface[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
lambda<- as.numeric(lambda)
p <- c(stigma_type[4], selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_surface[4], stigma_width[4], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
p <- as.numeric(p)
trait <- c("stigma_type","**selfing_rate**", "**pollen_size**", "mean_pollen_anther", "mean_ovules", "pollen_ovule_ratio", "stigma_area", "stigma_length", "**stigma_surface**", "**stigma_width**", "style_length", "style_width", "ovary_length",
           "ovary_width")
table<- data.frame(lambda,p, trait)
kable(table, format="markdown")
```

>>>>

lambda <- c(stigma_type[1], selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_surface[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1], si_index[1])
lambda<- as.numeric(lambda)
p <- c(stigma_type[4], selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_surface[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4],si_index[4])
p <- as.numeric(p)
trait <- c("stigma_type","**selfing_rate**", "**pollen_size**", "mean_pollen_anther", "mean_ovules", "pollen_ovule_ratio", "stigma_area", "stigma_length", "**stigma_surface**", "**stigma_width**", "style_length", "style_width", "ovary_length",
           "ovary_width")
table<- data.frame(lambda,p, trait)
colnames(table) <- c("Lambda", "P-value", "Traits")
kable(table, format="markdown")
```
